Importance sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body

### 2019-04-19 draft_p2.tex
Update table I in draft_p2.tex with new values from the least square fit of PDF_AVG
Add figure IS_GKTL and add it to .tex file

In section~\ref{sec:time_avg} we observed that extremely large values of the time-averaged drag can either result from a succession of rather typical---however all positive---fluctuations of the instantaneous drag $f_d$, or from a small number of extremely large fluctuations of the instantaneous drag.
In the latter case, each fluctuation typically lasts a correlation time $\tau_c$.
In this context, the \ac{gktl} algorithm is particularly suited to sample trajectories that display a succession of these fluctuations.
(\textbf{conclusion à développer.})
\begin{table}
  \centering
  \begin{tabular}{l|ccccc}
     & $\sigma$ & $2\sigma$ & $3\sigma$ & $4\sigma$ & $5\sigma$ \\
    \hline
    $k=0.02$ & 1594 & 799 & 155 & 22 & 0  \\ 
    $k=0.025$ 1019 & 834 & 521 & 198 & 27  \\ 
    $k=0.03$ & 539 & 510 & 391 & 205 & 36  \\ 
    $\mathcal{N}_{direct}$ & 2599.408 & 372.738 & 22.117 & 0.519 & 0.005  \\ 
  \end{tabular}
  \caption{Number of independent corresponding to fluctuations $F_{T_a} \geq a$ with a=$\sigma,2\sigma...$ in the biased ensemble, for the three experiments $k=0.02,0.025,0.03$. Parameters of the \ac{gktl} experiments are $N_c = 16384$, $T_a=10\tau_c$, $\tau = \tau_c /2$. Within the biased ensemble, trajectories are considered distinct if they overlap for less than $50\%$ of their duration.
    In addition, $\mathcal{N}_{direct}$ is the average number of fluctuations $F'_{T_a} \geq a$ on can expect from $N_c$ independent realisations of $F_{T_a}$, \textit{i.e.} with $k=0$.
    This number is based on the fact that the \ac{pdf} of $F_{T_a}$ is Gaussian.}
\label{tbl:nbTraj_tbl}
\end{table}

\begin{figure}
  \centering
%  \includegraphics[width=0.7\linewidth]{illustration_IS}
  \caption{\textbf{(a)}: Importance sampling for the time-averaged drag acting on the obstacle embedded in the test flow. The drag is averaged over $T=10\tau_c$. 
  The \ac{gktl} algorithm is used with $N_c = 16384$ copies and $T_a = T= 10\tau_c$ for three increasing values of the bias $k$. Additionally, the cloning period is $\tau = \tau_c/2$, resulting in $M=20$ iterations of the evolution/selection procedure. Note that in this particular example the last cloning stage at $t_{19}$ is not performed.
  As $k$ is increased, the sampled \ac{pdf} is shifted towards extreme values.
  Along the X-axis we display the fluctuation $F'_{T} = F_{T} - \overline{F_{T}}$, where the average $\overline{F_{T}}$ and standard deviation $\sigma_{T}$ have been computed over a timeseries spanning $10^6\tau_c$.
  One can see that the distribution for $k=0.03$ is peaked for a particular value of the fluctuation. This indicates that a significant part of the sampled trajectories actually overlap over the major part if their history.
  A a result, the average drag only differ by a small amount.}
\end{figure}

>>>>

In section~\ref{sec:time_avg} we observed that extremely large values of the time-averaged drag can either result from a succession of rather typical---however all positive---fluctuations of the instantaneous drag $f_d$, or from a small number of extremely large fluctuations of the instantaneous drag.
In the latter case, each fluctuation typically lasts a correlation time $\tau_c$.
In this context, the \ac{gktl} algorithm is particularly suited to sample trajectories that display a succession of these fluctuations.
(\textbf{conclusion à développer.})
\begin{table}
  \centering
  \begin{tabular}{l|ccccc}
     & $\sigma$ & $2\sigma$ & $3\sigma$ & $4\sigma$ & $5\sigma$ \\
    \hline
    $k=0.02$ & 1594 & 799 & 155 & 22 & 0  \\ 
    $k=0.025$ 1019 & 834 & 521 & 198 & 27  \\ 
    $k=0.03$ & 539 & 510 & 391 & 205 & 36  \\ 
    $\mathcal{N}_{direct}$ & 2601.258& 374.862& 24.268& 0.958& 0.000\\ 
  \end{tabular}
  \caption{Number of independent corresponding to fluctuations $F_{T_a} \geq a$ with a=$\sigma,2\sigma...$ in the biased ensemble, for the three experiments $k=0.02,0.025,0.03$. Parameters of the \ac{gktl} experiments are $N_c = 16384$, $T_a=10\tau_c$, $\tau = \tau_c /2$. Within the biased ensemble, trajectories are considered distinct if they overlap for less than $50\%$ of their duration.
    In addition, $\mathcal{N}_{direct}$ is the average number of fluctuations $F'_{T_a} \geq a$ on can expect from $N_c$ independent realisations of $F_{T_a}$, \textit{i.e.} with $k=0$.
    This number is based on the fact that the \ac{pdf} of $F_{T_a}$ is Gaussian.}
\label{tbl:nbTraj_tbl}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{IS_GKTL/IS_GKTL}
  \caption{Importance sampling for the time-averaged drag acting on the obstacle embedded in the test flow. The drag is averaged over $T=10\tau_c$. 
  The \ac{gktl} algorithm is used with $N_c = 16384$ copies and $T_a = T= 10\tau_c$ for three increasing values of the bias $k$. Additionally, the cloning period is $\tau = \tau_c/2$, resulting in $M=20$ iterations of the evolution/selection procedure.}
\end{figure}
